\bfseries\LARGE\singlespacing{Transmission of airborne respiratory infections with and without air cleaners in a Swiss school during non-pandemic conditions: A modeling study of epidemiological, environmental, and molecular data}

### 2023-06-21 doc/paper/manuscript.tex

\noindent At baseline, we collected aggregated data on age, sex and COVID-19 vaccination and recovery status in the participating classes. Daily we collected data on each absent student, \ie the absence, symptom onset and return date as well as the reason for the absence (sickness, career days,  or other) and symptoms. We also collected data on laboratory tests but none of the students reported a test result over the study. Based on the epidemiological data, we defined a case of respiratory infection as an absence where the student reported a sickness with at least one of the following symptoms: fever, coughing, tiredness, loss of test or smell, sore throat, headache, aches and pains, diarrhea, difficulty breathing or shortness of breath, stomach. Students were asked to report the first date when they experienced symptoms, \eg a student absent on Monday may report Saturday or Sunday as the symptom onset date. We will denote cases by their symptom onset date. Note that, during the week, the symptom onset date will usually correspond to the absence date, unless the student went to school despite experiencing symptoms. The line list data is shown in \supp~\zref{sec:case-data}. Informed consent of one student could not be obtained and his/her one absence was considered as unrelated to a respiratory infection. Reports about absences were entered electronically into a REDcap database\cite{Harris2009,Harris2019}. Furthermore, both classes participated in repetitive bi-weekly (Mondays and Wednesdays) testing for a panel of respiratory infections (see \nameref{sec:mol_analyses} below). The saliva samples were transported to the laboratory and stored at $-$80°C until further processed\cite{Galar2021,To2019,Huber2021}. \medskip

@@

\noindent Molecular analysis determined which saliva samples were positive for a respiratory pathogen. We analyzed the number of positive saliva samples with a Bayesian Multinomial logistic regression model (\supp~\zref{sec:multinomial-model}) where the expected number of positive samples for a pathogen was linked to the presence of air cleaners, adjusting for class-specific effects and the number of susceptibles for each pathogen. The latter was computed as the difference between the number of students per class and the cumulative number of positive samples. As a sensitivity analysis, we lagged the test results by one test date (\ie from Wednesday to Monday and from Monday to last Wednesday) and one test week (\ie from Monday to last Monday and Wednesday to last Wednesday), to consider the unknown delay when students were infected and tested positive.

>>>>

\noindent At baseline, we collected aggregated data on age, sex and COVID-19 vaccination and recovery status in the participating classes. Daily we collected data on each absent student, \ie the absence, symptom onset and return date as well as the reason for the absence (sickness, career days,  or other) and symptoms. We also collected data on laboratory tests but none of the students reported a test result over the study. Based on the epidemiological data, we defined a case of respiratory infection as an absence where the student reported a sickness with at least one of the following symptoms: fever, coughing, tiredness, loss of test or smell, sore throat, headache, aches and pains, diarrhea, difficulty breathing or shortness of breath, stomach. Students were asked to report the first date when they experienced symptoms, \eg a student absent on Monday may report Saturday or Sunday as the symptom onset date. We will denote cases by their symptom onset date. Note that, during the week, the symptom onset date will usually correspond to the absence date, unless the student went to school despite experiencing symptoms. The line list data is shown in \supp~\zref{sec:case-data}. Informed consent of one student could not be obtained and his/her one absence was considered as unrelated to a respiratory infection. Reports about absences were entered electronically into a REDcap database\cite{Harris2009,Harris2019}. Furthermore, both classes participated in repetitive bi-weekly (Tuesdays and Thursdays) testing for a panel of respiratory infections (see \nameref{sec:mol_analyses} below). The saliva samples were transported to the laboratory and stored at $-$80°C until further processed\cite{Galar2021,To2019,Huber2021}. \medskip

@@

\noindent Molecular analysis determined which saliva samples were positive for a respiratory pathogen. We analyzed the number of positive saliva samples with a Bayesian Multinomial logistic regression model (\supp~\zref{sec:multinomial-model}) where the expected number of positive samples for a pathogen was linked to the presence of air cleaners, adjusting for class-specific effects and the number of susceptibles for each pathogen. The latter was computed as the difference between the number of students per class and the cumulative number of positive samples. As a sensitivity analysis, we lagged the test results by one test date (\ie from Tuesday to last Thursday and from Thursday to Tuesday) and one test week (\ie from Tuesday to last Tuesday and Thursday to last Thursday), to consider the unknown delay when students were infected and tested positive.
